tall.---
title: "msc-phygeo-eo-ws-01-1"
author: "MOC - Environmental Observations (F. Detsch, C. Reudenbach, T. Nauss)"
date: "30 März 2017"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
source("C:/Users/tnauss/permanent/edu/msc-phygeo-environmental-observation/scripts/msc-phygeo-environmental-observation/src/functions/set_environment.R")
```

## Load environmental data (predictors)
Load stack of environmental variables.
```{r}
env_files <- list.files(path_rdata, pattern = glob2rx("r_*"), full.names = TRUE)

env <- lapply(env_files, function(f){
  readRDS(f)
})
env <- stack(env)
saveRDS(env, paste0(path_rdata, "s_env.rds"))
```

## Background sample as regular grid
```{r}
hessen <- readRDS(paste0(path_rdata, "v_hessen.rds"))
br <- sp::spsample(hessen, n = 10000, type = "regular")
br <- sp::SpatialPointsDataFrame(br, data.frame(NAME = rep("background", length(br))))
brfolds <- dismo::kfold(br, k=4)
br_train_test <- lapply(seq(4), function(i){
  test <- br[which(brfolds == i), ]
  train <- br[which(brfolds != i), ]
  list(training = train, test = test)
})

saveRDS(br, paste0(path_rdata, "v_br.rds"))
saveRDS(br_train_test, paste0(path_rdata, "br_train_test.rds"))
```


## Species sample random
```{r}
soc <- readRDS(paste0(path_rdata, "v_soc.rds"))
species <- unique(soc@data$NAME)

sr_train_test <- lapply(species, function(s){
  cur_soc <- soc[soc@data$NAME == s, ]
  cur_soc_folds <- dismo::kfold(cur_soc, k=4)
  sr_train_test <- lapply(seq(4), function(i){
    test <- cur_soc[which(cur_soc_folds == i), ]
    train <- cur_soc[which(cur_soc_folds != i), ]
    list(training = train, test = test)
  })
})
names(sr_train_test) <- species
saveRDS(sr_train_test, paste0(path_rdata, "sr_train_test.rds"))
```

## Compile species random/background random grid dataset
```{r}
br_train_test <- readRDS(paste0(path_rdata, "br_train_test.rds"))
sr_train_test <- readRDS(paste0(path_rdata, "sr_train_test.rds"))
species <- names(sr_train_test)

sr_br <- lapply(seq(length(sr_train_test)), function(s){
  cur_spec <- names(sr_train_test[s])
  cur_stt <- sr_train_test[[s]]
  train_test <- lapply(seq(length(cur_stt)), function(cs){
    
    train_occ <- cur_stt[[cs]]$training
    train_bgr <- br_train_test[[cs]]$training
    train_bgr@data$NAME <- paste(train_bgr@data$NAME, cur_spec, " ")
    
    test_occ <- cur_stt[[cs]]$test
    test_bgr <- br_train_test[[cs]]$test
    test_bgr@data$NAME <- paste(test_bgr@data$NAME, cur_spec, " ")
    
    training <- list(occurence = train_occ, background = train_bgr)
    test <- list(occurence = test_occ, background = test_bgr)
    return(list(training = training, test = test))
  })
  names(train_test) <- paste0("fold", seq(length(cur_stt)))
  return(train_test)
})
names(sr_br) <- species
sr_br

saveRDS(sr_br, paste0(path_rdata, "sr_br.rds"))
```

## Compile occurence data set using all samples
Use all occurence samples and create 10000 background samples from a regular 1000m grid all over Hessen.
```{r}
hessen <- readRDS(paste0(path_rdata, "v_hessen.rds"))
soc <- readRDS(paste0(path_rdata, "v_soc.rds"))

res = 1000
n = 10000

background_points <- raster::rasterToPoints(raster::raster(hessen, resolution = res), spatial = TRUE)
set.seed(11)
smpls <- sample(length(background_points), size = n)
background_points <- background_points[smpls, ]

bg_info <- data.frame(NAME = rep("Background", n),
                      TYPE = 0)
background_points <- SpatialPointsDataFrame(background_points, bg_info)

# Extract background data
background_env <- raster::extract(env, background_points, sp = TRUE)

# Extract species data
species <- unique(soc$NAME)
soc_all_env <- lapply(species, function(s){
  act <- raster::extract(env, soc[soc@data$NAME == s, ], sp = TRUE)
  act@data$TYPE = 1
  act <- rbind(act, background_env)
})
# mapview(soc_all_env[[1]], zcol = "NAME")

soc_all_env_df <- lapply(soc_all_env, function(s){
  df <- as.data.frame(s)
  df <- df[complete.cases(df), ]
  df$g100_clc12_V18_5 <- as.factor(df$g100_clc12_V18_5)
  df$FAD_eur_020m_fin <- as.factor(df$FAD_eur_020m_fin)
  df$FTY_eur_020m_fin <- as.factor(df$FTY_eur_020m_fin)
  return(df)
})

saveRDS(soc_all_env, paste0(path_rdata, "soc_all_env.rds"))
saveRDS(soc_all_env_df, paste0(path_rdata, "soc_all_env_df.rds"))

# soc_all_env <- readRDS(paste0(path_rdata, "soc_all_env.rds"))
```


## Compile occurence data set using samples from a 5000 m grid
Use only a maximum of one occurence sample within a 2500 m grid. Create 5000 background samples from a regular 2500m grid all over Hessen.
```{r}
hessen <- readRDS(paste0(path_rdata, "v_hessen.rds"))
soc <- readRDS(paste0(path_rdata, "v_soc.rds"))

res = 2500
n = 5000

background_points <- raster::rasterToPoints(raster::raster(hessen, resolution = res), spatial = TRUE)
set.seed(11)
smpls <- sample(length(background_points), size = n)
background_points <- background_points[smpls, ]

bg_info <- data.frame(NAME = rep("Background", n),
                      TYPE = 0)
background_points <- SpatialPointsDataFrame(background_points, bg_info)

# Extract background data
background_env <- raster::extract(env, background_points, sp = TRUE)

# Extract species data
sample_raster <- raster::raster(hessen, resolution = res)
species <- unique(soc$NAME)
soc_gs2500_env <- lapply(species, function(s){
  soc_gs2500_env <- dismo::gridSample(soc[soc@data$NAME == s, ], sample_raster, n = 1)
  soc_gs2500_env <- data.frame(NAME = s, soc_gs2500_env)
  return(soc_gs2500_env)
})
soc_gs2500_env <- do.call("rbind", soc_gs2500_env)
plyr::count(soc_gs2500_env$NAME)
soc_gs2500_env$TYPE = 1
coordinates(soc_gs2500_env) <- ~LON+LAT
raster::projection(soc_gs2500_env) <- projection(soc)



# Extract species data
species <- unique(soc_gs2500_env$NAME)
soc_gs2500_env <- lapply(species, function(s){
  act <- raster::extract(env, soc_gs2500_env[soc_gs2500_env@data$NAME == s, ], sp = TRUE)
  act <- rbind(act, background_env)
})
# mapview(soc_all_env[[1]], zcol = "NAME")


soc_gs2500_env_df <- lapply(soc_gs2500_env, function(s){
  df <- as.data.frame(s)
  df <- df[complete.cases(df), ]
  df$g100_clc12_V18_5 <- as.factor(df$g100_clc12_V18_5)
  df$FAD_eur_020m_fin <- as.factor(df$FAD_eur_020m_fin)
  df$FTY_eur_020m_fin <- as.factor(df$FTY_eur_020m_fin)
  return(df)
})
  
saveRDS(soc_gs2500_env, paste0(path_rdata, "soc_gs2500_env.rds"))
saveRDS(soc_gs2500_env_df, paste0(path_rdata, "soc_gs2500_env_df.rds"))
```






