tall.---
title: "msc-phygeo-eo-ws-01-1"
author: "MOC - Environmental Observations (F. Detsch, C. Reudenbach, T. Nauss)"
date: "30 März 2017"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
source("C:/Users/tnauss/permanent/edu/msc-phygeo-environmental-observation/scripts/msc-phygeo-environmental-observation/src/functions/set_environment.R")
```

## Get Corine etc. information
Download datasets from the European Environment Agency (EEA) on land-cover (CORINE), forest type (fty) and tree cover density (tcd) as well as a digital elevation model (dem) via <http://land.copernicus.eu/pan-european>. The projection is ETRS-LAEA, EPSG 3035. Convert all datasets to the project projection EPSG 25832. Use the Corine resolution of 100 m as a basis for all raster files. In order to speed things up, the corine as well as any other EEA dataset is croped to roughly the area of hessen first (bb_3035).

Compile Corine land-cover data.
```{r}
prj <- sp::CRS("+init=epsg:25832")
prj_corine <- sp::CRS("+init=epsg:3035")

hessen <- readRDS(paste0(path_rdata, "v_hessen.rds"))
bb_3035 <- sp::spTransform(hessen, prj_corine)
bb_3035 <- rgeos::gBuffer(bb_3035, width = 10000)
# mapview(bb_3035)

corine <- raster::raster(paste0(path_corine, "g100_clc12_V18_5.tif"))
projection(corine) <- prj_corine
corine <- raster::crop(corine, bb_3035)
corine <- raster::projectRaster(corine, res = 100, crs = prj, method = "ngb")

# mapview(corine)
saveRDS(corine, paste0(path_rdata, "r_corine.rds"))
# corine <- readRDS(paste0(path_rdata, "r_corine.rds"))
```

Compile forest type (fty) and additional information. Values in fty are 0 = non tree area, 1 = broadleved forest, 2 = coniferous forest, 254 = unclassifiable and 255 = outside area.
```{r}
fty <- raster::raster(paste0(path_forest, "FTY_eur_020m_fin.tif"))
projection(fty)
bb <- sp::spTransform(hessen, projection(fty))
bb <- rgeos::gBuffer(bb, width = 10000)
fty <- raster::crop(fty, bb)
fty <- raster::projectRaster(fty, corine, method="ngb")
# mapview(fty)
saveRDS(fty, paste0(path_rdata, "r_fty.rds"))
# fty <- readRDS(paste0(path_rdata, "r_fty.rds"))
```


Compile forest type additional information (fad). Values are 0 = non tree area, 3 = agricultural trees (broadleved), 4 = trees in urban context, 5 = trees in urban context, 254 = unclassifiable and 255 = outside area.
```{r}
fad <- raster::raster(paste0(path_forest, "FAD_eur_020m_fin.tif"))
projection(fad)
bb <- sp::spTransform(hessen, projection(fty))
bb <- rgeos::gBuffer(bb, width = 10000)
fad <- raster::crop(fad, bb)
fad <- raster::projectRaster(fad, corine, method="ngb")
# mapview(fad)
saveRDS(fad, paste0(path_rdata, "r_fad.rds"))
# fad <- readRDS(paste0(path_rdata, "r_fad.rds"))
```


Compile tree crown density data (tcd). Values 0 to 100 give the percentage density, 254 = unclassifiable and 255 = outside area.
```{r}
tcd <- raster::raster(paste0(path_forest, "TCD_eur_020m_fin.tif"))
projection(tcd)
bb <- sp::spTransform(hessen, projection(tcd))
bb <- rgeos::gBuffer(bb, width = 10000)
tcd <- raster::crop(tcd, bb)
tcd <- raster::projectRaster(tcd, corine, method="ngb")
# mapview(tcd)
saveRDS(tcd, paste0(path_rdata, "r_tcd.rds"))
# tcd <- readRDS(paste0(path_rdata, "r_tcd.rds"))
```

Compile digital elevation model (dem) data.
```{r}
dem_files <- list.files(paste0(path_raster, "dem"), pattern = glob2rx("*.TIF"), full.names = TRUE)
dem <- lapply(dem_files, function(f){
  r <- raster::raster(f)
  bb <- sp::spTransform(hessen, projection(r))
  bb <- rgeos::gBuffer(bb, width = 10000)
  r <- raster::crop(r, bb)
  r <- raster::projectRaster(r, corine, method="bilinear")
  return(r)
})
dem <- raster::merge(dem[[1]], dem[[2]])
names(dem) <- "dem"
# mapview(dem)
saveRDS(dem, paste0(path_rdata, "r_dem.rds"))
# dem <- readRDS(paste0(path_rdata, "r_dem.rds"))
```
